\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
edits.

\textit{Setup.} 
%\fengwei{I would suggest to add references for devices such as
%Pi, ATMEGA32U4 board, Yamazawa, etc.} 
As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board 
Computer inside \tool, which is powerful enough to process video data and has
an onboard WiFi chip. As for the HID Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
with USB protocol support, which is able to emulate multiple HID devices
with our modified firmware. About the USB 3.x Hub, we use one from the
UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripherals.
Apart from these essential parts, we also use an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
\mycircled{A} is a Huawei mobile phone as the victim's device; \mycircled{B} is a compact look of \tool prototype; \mycircled{1} is the USB 3.x Hub; \mycircled{2} is a Raspberry Pi 4B as the Single Board Computer; \mycircled{3} is an auxiliary power bank; \mycircled{4} is the Video Capture Card; \mycircled{5} is Atmel ATMEGA32U4 board as the HID Emulator. 
%\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
%2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
\fengwei{I think it is necessary to explain them in the text again.}

\begin{figure}[t]
	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}\\
	\begin{tabular}{ll}
	\circled[text=white,fill=myblue]{\scriptsize{A}} Victim's Device    &\circled[text=white,fill=myblue]{\scriptsize{B}}~\tool\\
	\circled[text=white,fill=myblue]{\footnotesize{1}} USB 3.x Hub        &\circled[text=white,fill=myblue]{\footnotesize{2}} Raspberry Pi 4B\\
	\circled[text=white,fill=myblue]{\footnotesize{3}} Auxiliary Power Bank &\circled[text=white,fill=myblue]{\footnotesize{4}} Video Capture\\
	\circled[text=white,fill=myblue]{\footnotesize{5}} ATMEGAA32U4 Board
	\end{tabular}

	\caption{\tool}
	\label{fig:armory}
\end{figure}

\subsection{Scripting mode}

In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as the
target device.  During this experiment, \tool disguised itself as a normal
keyboard and a home-brewed version of GoodUSB~\cite{tian2015defending} is
deployed to test the defense bypassing. We have tried to deploy the original
GoodUSB on the target device; as the GoodUSB is proposed in 2015, the code is
outdated and cannot be executed at modern OS; so we have to home-brew a similar
defense mechanism based on its paper~\cite{tian2015defending}.  In the
beginning, our home-brewed version of GoodUSB asked the victim to manually complete
a CAPTCHA to authorize the new USB device, a.k.a our \tool. But at this time,
by the design of GoodUSB, \fengwei{The following sentence is hard to
understand.}\hongyi{Fixed, removed redundant description} our \tool can already perform limited keystroke to complete the
CAPTCHA with the video stream from \tool. Up
to this point, the bypass of defense like GoodUSB is completed as our \tool
gains full function from the GoodUSB and becomes a trusted device. Then, our
\tool works similar to the original BadUSB, inserting keystroke to perform
arbitrary execution on the laptop. We tested three scripts, ranging from
reverse shell backdoor to malware payload execution, all of which resulting in
success.  With this experiment, we have proven the defense bypassing is successful
using \tool.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

>>>>

\textbf{Setup.} 
%\fengwei{I would suggest to add references for devices such as
%Pi, ATMEGA32U4 board, Yamazawa, etc.} 
As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board 
Computer inside \tool, which is powerful enough to process video data and has
an onboard WiFi chip. As for the HID Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
with USB protocol support, which is able to emulate multiple HID devices
with our modified firmware. About the USB 3.x Hub, we use one from the
UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripherals.
Apart from these essential parts, we also use an auxiliary power-bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our \tool prototype can be found in Figure~\ref{fig:armory}.
\mycircled{A} is a Huawei mobile phone as the victim's device; \mycircled{B} is a compact look of \tool prototype; \mycircled{1} is the USB 3.x Hub; \mycircled{2} is a Raspberry Pi 4B as the Single Board Computer; \mycircled{3} is an auxiliary power bank; \mycircled{4} is the Video Capture Card; \mycircled{5} is an Atmel ATMEGA32U4 board as the HID Emulator. 
%\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
%2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
\fengwei{I think it is necessary to explain them in the text again.}

\begin{figure}[t]
	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}\\
	\begin{tabular}{ll}
	\mycircled{A}Victim's Device    &\mycircled{B}\tool\\
	\mycircled{1}USB 3.x Hub        &\mycircled{2}Raspberry Pi 4B\\
	\mycircled{3}Auxiliary Power Bank &\mycircled{4}Video Capture\\
	\mycircled{5}ATMEGAA32U4 Board
	\end{tabular}

	\caption{\tool Prototype}
	\label{fig:armory}
\end{figure}

\subsection{HID Emulator Mode}

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as the
target device.  During this experiment, \tool disguised itself as a normal
keyboard and a home-brewed version of GoodUSB~\cite{tian2015defending} is
deployed to test the defense-bypassing. We have tried to deploy the original
GoodUSB on the target device; as the GoodUSB is proposed in 2015, the code is
outdated and cannot be executed at target device; so we have to home-brew a similar
defense mechanism based on its paper~\cite{tian2015defending}.  In the
beginning, our home-brewed version of GoodUSB asked the victim to manually complete
a CAPTCHA to authorize the new USB device, a.k.a our \tool. 
%But at this time,
%by the design of GoodUSB, 
%\fengwei{The following sentence is hard to
%understand.}\hongyi{Fixed, removed redundant description} 
However, our attack can enter keystrokes to complete the
CAPTCHA with the video stream by \tool. Up
to this point, the bypass of defense like GoodUSB is completed and our \tool
becomes a trusted device. Next, our
\tool works similar to the original BadUSB, inserting keystrokes to perform
arbitrary execution on the laptop. We tested three scripts, ranging from
reverse shell backdoor to malware payload execution, all of which resulting in
success. With this experiment, we have demonstrated the defense-bypassing is successful
using \tool.
%This also warned us that we need more thorough defense against such BadUSB
%attack.
